Distributions

### 2022-01-07 Ch2_distributions/Ch2_Figures.Rmd
Changed the order of figures.

```{r include=FALSE}
set.seed(20211207)

@@

@@

```{r include=FALSE}
# Color palette ----------------------------------------
my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012",
              "#0d907a","#b9bec3","#31aec5", "#653625", "#2C5C5D",
              "#DEB41E", "#2D3335", "#E2BF80", "#87A986", "#59879A",
              "#9C1D29", "#24716B", "#4a92b0")
scales::show_col(my.cols1)

my.cols2 <- c("#23262f", "#0d907a", "#DEB41E", 
              "#9C1D29", "#c76620", "#4a92b0",
              "#669e46", "grey")
scales::show_col(my.cols2)

## F1 - Color

Color version - each social group has a different color.

```{r Figure1col, fig.width=12, fig.height=4}

ind_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id, color = sgroup), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

fam_dens_plot <- ptpl %>%
  drop_na(sgroup) %>% 
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

plot_grid(b,a, labels = c("A)", "B)"))

@@

## F1 - BW

Black and white version seems more clear to me. Maybe worth including a different in the underlying curves to make sure the point comes across that one is for individuals, and the other for social groups.

```{r Figure1bw, fig.width=12, fig.height=4}

@@

Figure 1 - Kernel density estimates for the distribution of velocity data at different pooling levels, with the dark black density curve showing complete pooling. A) Partial pooling representation of the data, where each curve displays the density of velocities across a social group. B) No pooling scenario, where each density curve is associated to a single individual's velocity data. Plot inserts show a zoom to the tail of the distribution of velocity data in both panels. We observe considerable variation for both partial and no pooling scenarios, when compared to the single black density curve that represents the complete pooling. Particular focus towards the tails, where certain individuals possess much higher densities for large velocities, something that gets dampened when considering pooled data for velocity densities.

@@

```{r}
load("Ch2_distributions/Ch2_fits.RData")
```

```{r}
reg_fits_info %>% 
  dplyr::select(., dist, dBIC, ID, model) %>% 
  distinct() %>% 
  filter(., dBIC == 0) -> bestmodel

@@

```{r eval=FALSE}
# Difference to the second best model

@@

```{r}
# Calculate the BIC for the models:

@@

```{r}
cp.boot.fits %>% 
  dplyr::select(dist, bic, boot) %>% 
  distinct() %>% 
  transmute(dist = dist,
            BIC = bic,
            boot = boot,
            model = "CP") %>% 
  group_by(boot) %>% 
  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
  ungroup() -> cp.bic

@@

```{r}

@@

```{r eval=FALSE}

@@

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2, drop = FALSE) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist), size = 2.5) -> pooling.support

@@

pp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, group, boot) %>%
  group_by(group, boot) %>%
  distinct() %>%
  group_by(group) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = group, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "PP"),
             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
  scale_fill_manual(values = cols.fig2) -> pp.support

np.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots,
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "NP"),
             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
  scale_fill_manual(values = cols.fig2)  -> np.support

@@

```{r eval=FALSE}
# These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.

@@

cp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "") +
  theme(legend.position = "none") -> Fig4a

pp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "") +
  theme(legend.position = "none") -> Fig4b

np.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "BIC units from best model") -> Fig4c

@@

```{r fig.height=4}
cp.bic %>% 
  bind_rows(., pp.bic) %>% 
  bind_rows(., np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  facet_wrap(~model, nrow = 3) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15, size = 0.8) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") +
  theme(legend.position = "right") +
  guides(color=guide_legend(title = "Distribution \n model"))

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(minimum = min(min),
            median = median(min),
            mean = mean(min))

@@

# Figure X - Best fit parameters

```{r}

```{r FigureX, fig.height=9, fig.width=9}

colsx <- met.brewer("Tiepolo", n = 7)
aval <- 0.3

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  labs(subtitle = "PP - gamma") +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "PP - lnorm") +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "PP - weibull") +
  figx.theme -> pp.wei

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  labs(subtitle = "NP - gamma") +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "NP - lnorm") +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "NP - weibull") +
  figx.theme -> np.wei

legend.grid <- get_legend(pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=colsx) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  theme_bw() +
  guides(color = guide_legend(title = "Social Group", ncol = 2,
                              override.aes = list(alpha = 0.9, size = 5))))

ggsave2(filename = "Ch2_distributions/Figures/Figurex.png")
```

>>>>

```{r LoadMovData, include=FALSE}
set.seed(20211207)

@@

```{r Colors, include=FALSE}
# Color palette ----------------------------------------
my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012",
              "#0d907a","#b9bec3","#31aec5", "#653625", "#2C5C5D",
              "#DEB41E", "#2D3335", "#E2BF80", "#87A986", "#59879A",
              "#9C1D29", "#24716B", "#4a92b0")
scales::show_col(my.cols1)

my.cols2 <- c("#23262f", "#0d907a", "#DEB41E", 
              "#9C1D29", "#c76620", "#4a92b0",
              "#669e46", "grey")
scales::show_col(my.cols1)

# Colors for social groups ----------------------------------------

sgroup_col <- met.brewer("Tiepolo", n = 7)

# Colors for models ---------------------------------

mod_col <- met.brewer("Hokusai1", n=4)
mod_col <- c("#4C6838", "#C1B489", "#8EBF72", "#91A5A0")
mod_col <- c("#264653", "#2a9d8f", "#e2b33c", "#e76f51")

scales::show_col(mod_col)
```

@@

<!-- Color version - each social group has a different color.   -->

```{r Figure1col, fig.width=12, fig.height=4.5}

zoom_dims <- c(90, 200, 0, 0.01)
annot_xy <- c(50, 200, 0.025, 0.045)
box_color <- "blue"
aval <- 0.6

ind_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id, color = sgroup), stat = "density", alpha = aval, size=1) +
  #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", size = 1.3) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  #scale_color_manual(values = my.cols2) +
  scale_color_manual(values = sgroup_col) +
  theme(legend.position = "none")

@@

fam_dens_plot <- ptpl %>%
  drop_na(sgroup) %>% 
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = aval, size = 1) +
  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", size = 1.3) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  #scale_color_manual(values = my.cols2) +
  scale_color_manual(values = sgroup_col) +
  theme(legend.position = "none")

@@

toprow <- plot_grid(b,a, labels = c("A)", "B)"))

fig1leg <- get_legend(ptpl %>%
  drop_na(sgroup) %>% 
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = aval, size = 1.1) +
  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", size = 1.2) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  #scale_color_manual(values = my.cols2) +
  scale_color_manual(values = sgroup_col) +
    guides(color = guide_legend(title = "Social group",
                                override.aes = list(alpha = 0.8)))+
    theme(legend.position = "bottom"))

plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))

@@

<!-- ## F1 - BW  -->

<!-- Black and white version seems more clear to me. Maybe worth including a different in the underlying curves to make sure the point comes across that one is for individuals, and the other for social groups.   -->

```{r Figure1bw,  eval = FALSE, fig.width=12, fig.height=4}

@@

Figure 1 - Kernel density estimates for the distribution of velocity data at different pooling levels, with the dark black density curve showing complete pooling. A) Partial pooling representation of the data, where each curve displays the density of velocities across a social group. B) No pooling scenario, where each density curve is associated to a single individual's velocity data. Individuals belonging to the same social group share the line color. Plot inserts show a zoom to the tail of the distribution of velocity data in both panels. We observe considerable variation for both partial and no pooling scenarios, when compared to the single black density curve that represents the complete pooling. Particular focus towards the tails, where certain individuals possess much higher densities for large velocities, something that gets dampened when considering pooled data for velocity densities.

@@

```{r LoadFitData}
load("Ch2_distributions/Ch2_fits.RData")
```

```{r CalcBestModel}
reg_fits_info %>% 
  dplyr::select(., dist, dBIC, ID, model) %>% 
  distinct() %>% 
  filter(., dBIC == 0) -> bestmodel

@@

```{r BICdist, eval=FALSE}
# Difference to the second best model

@@

```{r CalcBICTable}
# Calculate the BIC for the models:

@@

```{r BootstrapBIC}
cp.boot.fits %>% 
  dplyr::select(dist, bic, boot) %>% 
  distinct() %>% 
  transmute(dist = dist,
            BIC = bic,
            boot = boot,
            model = "CP") %>% 
  group_by(boot) %>% 
  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
  ungroup() -> cp.bic

@@

```{r GenerateBICtable}

@@

```{r Generate_gt_Table, eval=FALSE}

@@

# Figure 2 - Best fit parameters

```{r Bootstrap_dBICzero}

```{r Figure2, fig.height=9, fig.width=9}

#colsx <- met.brewer("Tiepolo", n = 7)
aval <- 0.5

pp.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  labs(subtitle = "PP - gamma") +
  figx.theme -> pp.gam

pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "PP - lnorm") +
  figx.theme -> pp.ln

pp.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "PP - weibull") +
  figx.theme -> pp.wei

np.best %>% 
  filter(., dist == "gamma") %>% 
  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
  labs(subtitle = "NP - gamma") +
  figx.theme -> np.gam

np.best %>% 
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  labs(subtitle = "NP - lnorm") +
  figx.theme -> np.ln

np.best %>%
  filter(., dist == "weibull") %>% 
  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(5, 80), y = c(0, 2.1)) +
  labs(subtitle = "NP - weibull") +
  figx.theme -> np.wei

legend.grid <- get_legend(pp.best %>%
  filter(., dist == "lnorm") %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
  geom_point(alpha = aval) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
  theme_bw() +
  guides(color = guide_legend(title = "Social Group", ncol = 2,
                              override.aes = list(alpha = 0.9, size = 5))))

ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
```

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  #scale_fill_manual(values = cols.fig2, drop = FALSE) +
  scale_fill_manual(values = mod_col, drop = FALSE) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist), size = 2.5) -> pooling.support

@@

pp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, group, boot) %>%
  group_by(group, boot) %>%
  distinct() %>%
  group_by(group) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = group, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "PP"),
             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
  #scale_fill_manual(values = cols.fig2) +
  scale_fill_manual(values = mod_col, drop = FALSE) +
  NULL -> pp.support

np.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots,
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "NP"),
             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
  #scale_fill_manual(values = cols.fig2) +
  scale_fill_manual(values = mod_col, drop = FALSE) +
  NULL -> np.support

@@

```{r BICboxplots, eval=FALSE}
# These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.

@@

cp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  #scale_color_manual(values = cols.fig2) +
  scale_color_manual(values = mod_col, drop = FALSE) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "") +
  theme(legend.position = "none") -> Fig4a

pp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  #scale_color_manual(values = cols.fig2) +
  scale_color_manual(values = mod_col, drop = FALSE) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "") +
  theme(legend.position = "none") -> Fig4b

np.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  #scale_color_manual(values = cols.fig2) +
  scale_color_manual(values = mod_col, drop = FALSE) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap \n replicates", x = "BIC units from best model") -> Fig4c

@@

```{r Figure4, fig.height=4}
cp.bic %>% 
  bind_rows(., pp.bic) %>% 
  bind_rows(., np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  facet_wrap(~model, nrow = 3) +
  #geom_col() +
  geom_point(alpha = 0.9, shape = 15, size = 0.9) +
  #scale_color_manual(values = cols.fig2) +
  scale_color_manual(values = mod_col, drop = FALSE) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") +
  theme(legend.position = "right") +
  guides(color=guide_legend(title = "Distribution \n model", override.aes = list(size = 5)))

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(minimum = min(min),
            median = median(min),
            mean = mean(min),
            q2.5 = quantile(min, probs = 0.025),
            q97.5 = quantile(min, probs = 0.975))

@@
